Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | AI & digital&nbsp;humanities&nbsp;instructor </font>

### 2023-09-06 index.Rmd
papers

<div class="container-fluid">
<div class="row">
  <div class="col-sm-7">
  <iframe src="news.html" width="100%" height="200" style="border: none;"></iframe>
  </div>
  <div class="col-sm-5">
  <a class="twitter-timeline" 
  data-show-screen-name="false" 
  data-lang="en" 
  data-width="399px" 
  data-height="200px" 
  href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw"
  data-chrome="noheader nofooter">
  " "
  </a> 
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
  </div>
</div>

@@

### What I do  <IMG SRC="round.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 20%; height: auto;">
<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, on art history and creative industries and advising collaborative projects between involving academic and media industry partners.<br>
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do workshops on **R, stats & data visualization** and **AI**-related things (see [more here](https://datafigure.eu)).

@@

@@

@@

Email: andres.karjus --at-- tlu.ee <br>
Twitter: <a href="https://twitter.com/AndresKarjus">https://twitter.com/AndresKarjus</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>https://mastodon.social/@AndresKarjus</a>
<br>
</div>

>>>>

<div class="container-fluid">
<div class="row">
  <div class="col-sm-7">
  <iframe src="news.html" width="100%" height="200" style="border: none;"></iframe>
  </div>
  <!---
  <div class="col-sm-5">
  <a class="twitter-timeline" 
  data-show-screen-name="false" 
  data-lang="en" 
  data-width="399px" 
  data-height="200px" 
  href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw"
  data-chrome="noheader nofooter">
  " "
  </a> 
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
  </div>
  -->
  <IMG SRC="round.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 20%; height: auto;">
</div>

@@

### What I do  
<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, on art history and creative industries and advising collaborative projects between involving academic and media industry partners.<br>
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do workshops on **R, stats & data visualization** and **AI**-related things (see [more here](https://datafigure.eu)).

@@

* Andres Karjus and Christine Cuskley. 2023. Evolving Linguistic Divergence on Polarizing Social Media | arXiv [preprint](https://arxiv.org/abs/2309.01659)

@@

* Oiva, Mila, Ksenia Mukhina, Vejune Zemaityte, Tillmann Ohm, Mikhail Tamm, Andres Karjus, Mark Mets, Daniel Chávez Heras Mar Canet Solà, Helena Hanna Juht, Maximilian Schich. 2023. A Framework for the Analysis of Historical Newsreels | [preprint](https://doi.org/10.31235/osf.io/a4xsp)

@@

Email: andres.karjus --at-- tlu.ee <br>
Twitter: <a href="https://twitter.com/AndresKarjus">https://twitter.com/AndresKarjus</a> <br>
Mastodon: <a href=https://mastodon.social/@andreskarjus>https://mastodon.social/@AndresKarjus</a>
<br>
LinkedIn: <a href="https://www.linkedin.com/in/andreskarjus/">https://www.linkedin.com/in/andreskarjus/</a> <br> 
</div>

### 2023-09-06 news.Rmd
papers

@@

- Published an opinion piece in the popular science outlet [Novaator](https://novaator.err.ee/1609007981/andres-karjus-tehisintellekt-seab-juba-sel-sugisel-koolid-sundvaliku-ette) on how generative AI will affect education in the near future (16.06.2023)

>>>>

- Two new preprints this week: ["Evolving Linguistic Divergence on Polarizing Social Media"](https://arxiv.org/abs/2309.01659) and ["A Framework for the Analysis of Historical Newsreels"](https://doi.org/10.31235/osf.io/a4xsp)  (06.09.2023)

@@

- Published an opinion piece in the popular science outlet [Novaator](https://novaator.err.ee/1609007981/andres-karjus-tehisintellekt-seab-juba-sel-sugisel-koolid-sundvaliku-ette) on how generative AI will affect education in the near future (in Estonian; 16.06.2023)
